Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development

### 2017-01-11 jssst/reply_letter.tex
Modify the reply letter

% cover letter
\begin{flushleft}
  2017-01-13\newline 
  ソフトウェア論文特集\newline
  論文・記事番号：16-S-05\newline
  題目：Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development\newline
  著者: Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi\newline
\end{flushleft}
\textbf{Dear Editor and Reviewer,}\newline

We highly appreciate the insightful suggestions and detailed valuable comments on our paper. 
The suggestions of the reviewers are very helpful for us and the suggestions are now incorporated in the revised paper as follows.
We have attached the last paper review and revised paper in our reply letter.
We hope the editor and the reviewers will be satisfied with our replies to the comments and the revised paper.\newline\newline

\begin{flushleft}
  Yours sincerely,\newline

  Takuro Yamamoto\newline
  Osaka University\newline
  Email address: t-yamamoto@hopf.sys.es.osaka-u.ac.jp\newline
\end{flushleft}

\clearpage

@@

\newpage

>>>>

% cover letter
\begin{flushleft}
  2017-01-13\newline 
  ソフトウェア論文特集\newline
  論文・記事番号：16-S-05\newline
  題目：Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development\newline
  著者: Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi\newline

@@
